Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline

### 2017-05-01 draft/ms_v5.tex
Small section about the b parameter bug

%% ------------------------------------------------------------------------------------ %%
\title{Characterization and Photometric Performance of the Hyper Suprime-Cam 
       Software Pipeline.}

@@

    The Subaru Strategic Program (SSP) is an ambitious wide-area, multi-band survey
    using the Hyper Suprime-Cam (HSC) on the Subaru telescope. 
    The Wide layer of the SSP is both wide and deep, reaching a detection limit of 
    $i{\sim}26.0$ mag. 
    At these depths, it is challenging to achieve accurate, unbiased, and consistent
    photometry across all five bands. 
    The HSC data are reduced using a pipeline that builds on the prototype pipeline 
    being designed by the Large Synoptic Survey Telescope’s Data Management system. 
    We have developed a \texttt{Python}-based, flexible framework to inject synthetic
    galaxies into real HSC images called \synpipe{}. 
    In this paper, we explain the design and implementation of \synpipe{} and generate 
    a sample of synthetic galaxies to examine the photometric performance of the HSC
    pipeline. 
    For stars, we achieve 1\% photometric precision at $i{\sim}19.0$ mag and 7\%
    precision at $i{\sim}25.0$ in the $i$-band (corresponding to statistical scatters 
    of ${\sim}0.01$ and ${\sim}0.05$ mag respectively).  
    For synthetic galaxies with single-\ser{} profiles, forced \cmodel{} photometry
    achieves 9\% photometric precision at $i{\sim}20.0$ mag and 13\% precision at 
    $i{\sim}25.0$ in the $i$-band (corresponding to statistical scatters of 
    ${\sim}0.15$ and ${\sim}0.22$ mag respectively). 
    We show that both \forced{} PSF and \cmodel{} photometry yield unbiased color 
    estimates that are robust to seeing conditions. 
    We identify several caveats that apply to the version of HSC pipeline used for 
    the first public HSC data release (DR1) that need to be taking into consideration. 
    First, the degree to which an object is blended with other objects impacts the 
    overall photometric performance.  
    This is especially true for point sources. 
    Highly blended objects tend to have larger photometric uncertainties, 
    systematically underestimated fluxes and slightly biased colors. 
    Second, $>20$\% of stars at $22.5< i < 25.0$ mag can be misclassified as 
    extended objects.
    Third, the current \cmodel{} algorithm tends to strongly underestimate the 
    half-light radius and ellipticity of galaxy with $i>21.5$ mag.

@@

    By definition, the parameter is bound from 0 to 1.
    When the deblending process is carried out correctly, the $b({\rm A})$ parameter
    reflects the fraction of fluxes that comes from other objects in the
    region of ${\rm A}$.
%% ------------------------------------------------------------------------------------ %%

>>>>

%% ------------------------------------------------------------------------------------ %%
\title{Characterization and Photometric Performance of the Hyper Suprime-Cam 
       Software Pipeline}

@@

    The Subaru Strategic Program (SSP) is an ambitious multi-band survey
    using the Hyper Suprime-Cam (HSC) on the Subaru telescope. 
    The Wide layer of the SSP is both wide and deep, reaching a detection limit of 
    $i{\sim}26.0$ mag. 
    At these depths, it is challenging to achieve accurate, unbiased, and consistent
    photometry across all five bands. 
    The HSC data are reduced using a pipeline that builds on the prototype pipeline 
    for the Large Synoptic Survey Telescope. 
    We have developed a \texttt{Python}-based, flexible framework to inject synthetic
    galaxies into real HSC images called \synpipe{}. 
    Here we explain the design and implementation of \synpipe{} and generate 
    a sample of synthetic galaxies to examine the photometric performance of the HSC
    pipeline. 
    For stars, we achieve 1\% photometric precision at $i{\sim}19.0$ mag and 7\%
    precision at $i{\sim}25.0$ in the $i$-band (corresponding to statistical scatters 
    of ${\sim}0.01$ and ${\sim}0.05$ mag respectively).  
    For synthetic galaxies with single-\ser{} profiles, forced \cmodel{} photometry
    achieves 9\% photometric precision at $i{\sim}20.0$ mag and 13\% precision at 
    $i{\sim}25.0$ in the $i$-band (corresponding to statistical scatters of 
    ${\sim}0.15$ and ${\sim}0.22$ mag respectively). 
    We show that both \forced{} PSF and \cmodel{} photometry yield unbiased color 
    estimates that are robust to seeing conditions. 
    We identify several caveats that apply to the version of HSC pipeline used for 
    the first public HSC data release (DR1) that need to be taking into consideration. 
    First, the degree to which an object is blended with other objects impacts the 
    overall photometric performance.  
    This is especially true for point sources. 
    Highly blended objects tend to have larger photometric uncertainties, 
    systematically underestimated fluxes and slightly biased colors. 
    Second, $>20$\% of stars at $22.5< i < 25.0$ mag can be misclassified as 
    extended objects.
    Third, the current \cmodel{} algorithm tends to strongly underestimate the 
    half-light radius and ellipticity of galaxy with $i>21.5$ mag.

@@

    By definition, the parameter is bound from 0 to 1.
    When the deblending process is carried out correctly, the $b({\rm A})$ parameter
    reflects the fraction of fluxes that comes from other objects in the
    region of ${\rm A}$.

    The current version of \hscpipe{} contains a bug related to the calculation of $b$
    parameter. 
    For bright object (e.g. $i<23.0$ mag), its effect can be ignored.  
    For fainter object, it mostly leads to underestimate of $b$ parameter by $< 12$\%, 
    especially for objects with $-3.5 < \log_{10} b < -1.5$. 
    This bug has been fixed for the future release of \hscpipe{} and HSC survey data. 
    For the \synpipe{} tests here, it does not qualitatively change the conclusions 
    related to the highly-blended objects and about the relationship between $b$ and
    photometric precision. 
    Please see Murata\etal (in prep.) and Bosch\etal (in prep.) for more details.
